---
title: "Glamour Theming Demo"
format:
  html:
    self-contained: true
    code-fold: true
    theme: cosmo
execute:
  warning: false
  message: false
---

## Setup

Load the package via `devtools::load_all()` and initialize fonts.

```{r setup}
library(ggplot2)
library(ggtext)

# Load all glamour functions from the package source
devtools::load_all()

# Register Google Fonts and activate showtext rendering
load_glamour_fonts()
```

---

## Palettes

```{r palettes, fig.height=1.8}
show_palette("warm")
show_palette("slate")
show_palette("midnight")
```

---

## 1 · Scatter Plot — Colored Title Replaces Legend

The Glamour of Graphics principle: encode your groups in the title using
`color_label()`, then set `legend = "none"`.

```{r scatter, fig.width=8, fig.height=5}
pal <- glamour_palette("warm")

ggplot(mpg, aes(displ, hwy, color = drv)) +
  geom_point(alpha = 0.8, size = 2.5) +
  scale_color_manual(
    values = c(
      "f" = pal[["accent1"]],
      "r" = pal[["accent2"]],
      "4" = pal[["accent3"]]
    )
  ) +
  labs(
    title = paste(
      color_label("Front-wheel", pal[["accent1"]]),
      "cars are most efficient;",
      color_label("rear-wheel", pal[["accent2"]]),
      "the least"
    ),
    subtitle = color_legend(c(
      "Front-wheel" = pal[["accent1"]],
      "Rear-wheel"  = pal[["accent2"]],
      "4WD"         = pal[["accent3"]]
    )),
    x = "Engine displacement (L)",
    y = "Highway MPG",
    caption = "Source: ggplot2::mpg"
  ) +
  theme_glamour(palette = "warm", legend = "none")
```

---

## 2 · Bar Chart — Horizontal with Grid Lines

Flip coordinates to avoid head-tilting on category labels.
Use a light horizontal grid to aid reading bar lengths.

```{r bar, fig.width=8, fig.height=5}
pal <- glamour_palette("slate")

mpg |>
  dplyr::summarise(mean_hwy = mean(hwy), .by = class) |>
  dplyr::arrange(mean_hwy) |>
  dplyr::mutate(class = forcats::fct_inorder(class)) |>
  ggplot(aes(mean_hwy, class)) +
  geom_col(fill = pal[["accent1"]], width = 0.7) +
  geom_text(
    aes(label = round(mean_hwy, 1)),
    hjust = -0.2,
    size  = 3,
    family = glamour_fonts()[["sans"]],
    color  = pal[["ink"]]
  ) +
  labs(
    title    = "Compact and subcompact cars lead on highway MPG",
    subtitle = "Mean highway miles per gallon by vehicle class",
    x        = NULL,
    y        = NULL,
    caption  = "Source: ggplot2::mpg"
  ) +
  scale_x_continuous(expand = expansion(mult = c(0, 0.12))) +
  theme_glamour(palette = "slate", grid = "x")
```

---

## 3 · Line Chart — Dark Background

Switch to the `"midnight"` palette for presentation-style slides.

```{r line, fig.width=8, fig.height=5}
pal <- glamour_palette("midnight")

economics |>
  dplyr::filter(date >= as.Date("2000-01-01")) |>
  ggplot(aes(date, unemploy / pop)) +
  geom_line(color = pal[["accent1"]], linewidth = 1) +
  geom_area(fill = pal[["accent1"]], alpha = 0.15) +
  labs(
    title    = "Unemployment spiked sharply during the 2008 financial crisis",
    subtitle = "Unemployed persons as a share of total US population, 2000–present",
    x        = NULL,
    y        = NULL,
    caption  = "Source: ggplot2::economics"
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 100)) +
  theme_glamour(palette = "midnight")
```

---

## 4 · Faceted Plot

Faceting with stripped backgrounds and bold strip labels.

```{r facet, fig.width=9, fig.height=5}
pal <- glamour_palette("warm")

ggplot(mpg, aes(displ, hwy)) +
  geom_point(color = pal[["accent1"]], alpha = 0.7, size = 2) +
  geom_smooth(
    method = "lm", se = FALSE,
    color = pal[["accent2"]], linewidth = 0.8
  ) +
  facet_wrap(~drv, labeller = labeller(
    drv = c("f" = "Front-wheel", "r" = "Rear-wheel", "4" = "4WD")
  )) +
  labs(
    title    = "The displacement–efficiency relationship holds across all drive types",
    subtitle = "Linear trend overlaid; shading removed to reduce ink",
    x        = "Engine displacement (L)",
    y        = "Highway MPG",
    caption  = "Source: ggplot2::mpg"
  ) +
  theme_glamour(palette = "warm", grid = "y")
```
